SI: Settlements

### 2021-09-16 analysis/paper/paper.Rmd
model based clustering

>>>>

## Groups in the data

This is not done for pottery traditions due to an error in one of the periods/
regions that is caused by not enough variance in the PCA data. Weird...

```{r mclust2-neo}
mb_clust2 <- pca2_neo %>% mbc_cluster()

mb_clust2 %>% pull(classif)

mb_clust2 %>%
    select(classif) %>% 
    ungroup(c(reg, neo)) %>%
  unnest() %>% View()
    mutate(g = str_c(reg, g))

mb_classif2_neoB <- mb_clust2 %>% mbc_classify("NeoB")
mb_classif2_neoC <- mb_clust2 %>% mbc_classify("NeoC")

(mb_classif2_neoB == mb_classif2_neoC) %>% all()

# bind_cols(mb_clustering_neo2$x[[2]][, 1:2], mb_clustering_neo2$classif[[2]]) %>% 
#   ggplot(aes(PC1, PC2, color = factor(g))) +
#   stat_ellipse() +
#   geom_point() +
#   theme_bw() +
#   facet_wrap(vars(g))

mb_map2_neoB <- mb_classif2 %>% mbc_map(sf = settlements2, neo = "NeoB")
mb_map2_neoC <- mb_classif2 %>% mbc_map(sf = settlements2, neo = "NeoC")

# boxploty pro proměnné ve skupinách...
```

```{r mclust2-map-neoB, fig.cap="Clusters in pottery groups in Neolithic B."}
mb_map2_neoB
```

```{r mclust2-map-neoC, fig.cap="Clusters in pottery groups in Neolithic C."}
mb_map2_neoC
```

```{r}
res2_long %>% 
  filter(variable != "cont") %>% 
  add_neo() %>% 
  right_join(mb_classif2, by = c("id", "neo")) %>% 
  filter(neo == "NeoC") %>% 
  ggplot(aes(g, value, color = g))+
  geom_boxplot(show.legend = FALSE) +
  facet_wrap(vars(variable), scales = "free_y", ncol = 2) +
  theme_minimal()
```
